\documentclass[11pt,letterpaper]{article}
\usepackage[osf]{mathpazo}
\usepackage[scaled=0.86]{berasans}
\usepackage[scaled=1.03]{inconsolata}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[ManyBibs]{currvita}
\usepackage{bibunits}
\usepackage[pdfborder={0 0 0},breaklinks]{hyperref}
\usepackage{fullpage}
\usepackage{trace}
\usepackage{xcolor}

\definecolor{oberlinred}{RGB}{207,16,47}
\definecolor{oberlingold}{RGB}{255,184,29}
\renewcommand*\cvheadingfont{\Large\bfseries\color{oberlinred}}
\renewcommand*\cvlistheadingfont{\large\bfseries\color{oberlinred}}

% Use \privatetrue to typeset a bibliography containing private stuff.
\newif\ifprivate
%\privatetrue

\hypersetup{
	pdftitle={Checkoway Curriculum Vitae},
	pdfauthor={Stephen Checkoway},
}

\urlstyle{sf}
\newenvironment{cvseclist}[1]
	{\phantomsection
	\addcontentsline{toc}{section}{#1}%
	\begin{cvlist}{#1}}
	{\end{cvlist}}
	

% taken from hs's mary.tex, and tracing back to knuth.
\def\dash---{\kern.16667em---\penalty\exhyphenpenalty\hskip.16667em\relax}

\cvplace{Oberlin College}

\newcommand*\personalline[2]{%
	\leavevmode
	\hbox to14pc{#1\hfil}%
	\hskip1pc
	\hbox{#2}%
}

\defaultbibliography{checkoway}
\defaultbibliographystyle{unsrtabbrv}

\newcommand\multilinelabel[1]{%
	\smash{\parbox[t]{\cvlabelwidth}{\raggedright #1}}%
}

\makeatletter
\newcommand*\pubs[2]{%
	\item[\multilinelabel{#1}]
	\begin{bibunit}%
		\nocite{#2}%
		\putbib
		%\immediate\write\@bibunitaux{\string\bibdata{\bu@bibdata}}%
	\end{bibunit}%
	%\immediate\write18{bibtex \@bibunitname}%
	%\InputIfFileExists{\@bibunitname.bbl}{}
	%	{Run \texttt{bibtex \@bibunitname}}%
	\IfFileExists{\@bibunitname.bbl}{}{Run \texttt{bibtex
	\@bibunitname}}%
}
\makeatother

\newcommand*\ta[2]{%
	#1%
	\if\relax#2\relax\else
		\\Course Web: \url{#2}%
	\fi
	\par
}

\newcommand*\email[1]{\href{mailto:#1}{\sffamily#1}}

\begin{document}
\begin{cv}{Stephen Checkoway\hfill Curriculum Vit\ae}
\begin{cvseclist}{Personal}
	\item
	\personalline{Oberlin College Computer Science}{Tel.: +1 445.775.8364}\\
	\personalline{10 N. Professor St.}{Email: \email{stephen.checkoway@oberlin.edu}}\\
	\personalline{Oberlin, OH 44047-1019}{Web: \url{https://checkoway.net}}
\end{cvseclist}

\iffalse
\begin{cvseclist}{Research Interests}
	\item My primary research interests are in systems security
	and voting\dash---particularly in voting security. Beyond
	those, I am interested in a number of topics such as tech
	policy\dash---particularly 4th amendment protections against
	unreasonable searches and seizures as it relates to
	computers\dash---modern algebra, category theory,
	cryptography, programming languages, and compilers.
\end{cvseclist}
\fi

\begin{cvseclist}{Appointments}
	\item[7/2019--current] Assistant Professor, Oberlin College
	\item[11/2018--6/2019] Research Specialist, Oberlin College
	\item[7/2018--6/2019] Affiliate Scholar, Oberlin College
	\item[8/2015--7/2018] Assistant Professor, University of
	Illinois at Chicago
	\item[8/2012--7/2015] Assistant Research Professor, Johns Hopkins
	University.
\end{cvseclist}

\begin{cvseclist}{Education}
	\item[9/2005--6/2012] University of California San Diego.\\
	M.S., C.Phil., and Ph.D. in computer science.\\Advisor: Hovav
	Shacham.
	\item[9/2001--6/2005] University of Washington.\\
	B.S. in mathematics; B.S. in computer science; minor in
	physics.
\end{cvseclist}

\begin{cvseclist}{Grants and gifts}
	\item[10/2016--9/2021] National Science Foundation.
	\textit{CPS: Synergy: Collaborative Research: Foundations of Security
	Cyber-Physical Systems of Systems.}
	PI.
	Award number: CNS-1646063.
	Award: \$240,000 (\$800,000 total project award).
	\item[9/2015] Mozilla Foundation.
	\textit{Identify and preventing timing side-channel attacks.}
	PI.
	Gift: \$61,000 (\$67,115 total gift).
	\item[12/2013] Mozilla Foundation.
	\textit{Securing the TLS Protocol.}
	PI.
	Gift: \$65,433 (50\% share).
	\item[9/2013--8/2018] National Science Foundation.
	\textit{TWC: Frontier: Collaborative: Enabling Trustworthy
	Cybersystems for Health and Wellness.}
	Co-PI.
	PI: Aviel Rubin.
	Award number: CNS-1329737.
	Award: \$2,000,000 (\$10,000,000 total project award).
	(My involvement ended 7/2015.)
	\item[9/2013--9/2014] Department of Defense.
	\textit{Teaching Real-world Tools and Techniques for Reverse
	Engineering.}
	PI.
	Award number: 115519.
	Award: \$77,996.
\end{cvseclist}

\begin{cvseclist}{Publications}
	%\renewcommand*\cvlabelfont{\slshape}
	% Amusing hack. private.bib contains LaTeX code to typeset the
	% bibliographic database it contains. If the file doesn't
	% exist, then TeX relaxes.
	\InputIfFileExists{private.bib}\relax\relax
	\pubs{Refereed papers}{
		johnson-et-al:jetset:usenix21,
		sun-et-al:kollector:tmc,
		crow-et-al:triton-testbed:cset19,
		ghasemisharif-et-al:ssoff:security18,
		martin-et-al:sentinel:iotdi18,
		checkoway-et-al:juniper-dual-ec:ccs16,
		rushanan-checkoway:run-dma:woot15,
		lundberg-et-al:mcis:ccs14,
		checkoway-et-al:dualec:usenix14,
		brocker-checkoway:iseeyou:usenix14,
		mowery-et-al:radsec:usenix14,
		tice-et-al:fcfi:usenix14,
		checkoway-shacham:iago:asplos13,
		sarwate-checkoway-shacham:nonplurality:spp13,
		checkoway:accessopen:tinytocs12,
		checkoway-et-al:cars-connectivity:usenix11,
		meiklejohn-et-al:tolling:usenix11,
		kanich-checkoway-mowery:HIT:woot11,
		checkoway-et-al:noret:ccs10,
		checkoway-sarwate-shacham:single-ballot:evt10,
		koscher-et-al:car:oakland10,
		checkoway-shacham-rescorla:texhack:leet2010,
		checkoway-et-al:avc-security:evt09,
		zhang-et-al:trace-cache:iccd06%
	}
	\pubs{Dissertation and reports}{
		checkoway:dissertation:2012,
		martin-et-al:classifying-network-protocol,
		sarwate-checkoway-shacham:auditing-alternatives:ucsd11,
		checkoway-shacham:noret:ucsd10,
		checkoway:auditing:re08%
	}
	\pubs{Articles}{
		checkoway-et-al:juniper-dual-ec:cacm,
		checkoway-shacham-rescorla:texhack:login2010%
	}
\end{cvseclist}

\begin{cvseclist}{Invited talks}
	\item Oberlin College. ``Electronic Voting Security.'' Oct.\ 2018.

	\item Fastly Security Speaker Series. ``A Systematic Analysis of the
	Juniper Dual EC Incident.'' Oct.\ 2017.

	\item IRTF Applied Networking Research Prize talk at IETF 99. ``A
	Systematic Analysis of the Juniper Dual EC Incident. Jul.\ 2017.

	\item Code Freeze 2015: Security keynote.
	``Embedded Systems Security: The Need for a Holistic
	Approach.'' Jan.\ 2015.
	
	\item Oberlin College. ``iSeeYou:
	Disabling the MacBook webcam indicator LED.'' Oct.\ 2013.
	
	\item National Cable \& Telecommunications Association.
	``Electronic Voting Security.'' Apr.\ 2013.
	
	\item Case Western Reserve University. ``Motors, Voters, and
	the Future of Embedded Security.'' Nov.\ 2012.

	\item Messaging Malware Mobile Anti-Abuse Working Group,
	keynote. ``Electronic Voting Security.'' Oct.\ 2012.

	\item Workshop on Embedded System Security keynote, joint talk
	with Karl Koscher. ``Experimental Security Analysis of a
	Modern Automobile.'' Oct.\ 2011.
\end{cvseclist}


\begin{cvseclist}{Professional Activities}
	\item[Editorial board] JETS 2013--present.
	\item[\multilinelabel{Program committees}]
	      USENIX Security 2014, 2015, 2016, 2017, 2019, 2020
	\item IEEE Security \& Privacy 2016, 2017, 2020
	\item USENIX CSET 2013, 2019, 2020
	\item AutoSec 2019, 2021
	\item IEEE LangSec 2018
	\item ROOTS 2017, 2018
	\item WWW 2016, 2017
	\item ACM CCS 2014, 2015
	\item CANS 2015
	\item PASSAT 2014
	\item ARES 2014
	\item USENIX WOOT 2011, 2013
	\item DIMVA 2012
	\item USENIX EVT/WOTE 2011, 2012
\end{cvseclist}

\newcommand\class{%
	\\
	\null
	\qquad
}
\begin{cvseclist}{Teaching}
	\item[At Oberlin] Programming Abstractions
		\class Summer 2021
		\url{https://checkoway.net/teaching/cs275/2021-summer/}
		\class Fall 2020
		\url{https://checkoway.net/teaching/cs275/2020-fall/}
	\item Computer Organization
		\class Spring 2021 (co-taught)
	\item Computer and Information Security
		\class Fall 2020
		\url{https://checkoway.net/teaching/cs343/2020-fall/}
	\item Systems Programming
		\class Spring 2020
		\url{https://checkoway.net/teaching/cs241/2020-spring/}
		\class Fall 2019
		\url{https://checkoway.net/teaching/cs241/2019-fall/}
	\item[At UIC] Languages and Automata
		\class Spring 2018
		\url{https://checkoway.net/teaching/cs301/2018-spring/}
		\class Fall 2015
		\url{https://checkoway.net/teaching/cs301/2015-fall/}
	\item Secure Computer Systems
		\class Fall 2017
		\url{https://checkoway.net/teaching/cs487/2017-fall/}
	\item Research Methods in Computer Science
		\class Spring 2017
		\url{https://checkoway.net/teaching/cs590/2017-spring/}
	\item Software Vulnerability Analysis
		\class Fall 2016
		\url{https://checkoway.net/teaching/cs491/2016-fall/}
	\item Advanced Computer Security
		\class Spring 2016
		\url{https://checkoway.net/teaching/cs594/2016-spring/}

	\item[At JHU] Automata and Computation Theory
		\class Spring 2015
		\url{https://checkoway.net/teaching/cs271/2015-spring/}
		\class Spring 2014
		\url{https://checkoway.net/teaching/cs271/2014-spring/}
	\item Software Vulnerability Analysis
		\class Fall 2014
		\url{https://checkoway.net/teaching/cs460/2014-fall/}
		\class Fall 2013
		\url{https://checkoway.net/teaching/cs460/2013-fall/}
		\class Fall 2012
		\url{https://checkoway.net/teaching/cs460/2012-fall/}
	\item Advanced Topics in Software Security
		\class Spring 2013
		\url{https://checkoway.net/teaching/cs668/2013-spring/}
\end{cvseclist}

%\begin{cvseclist}{Invited Lectures}
%	\item[11/2011] \emph{Experimental Security Analysis of a Modern
%	Automobile}. Part of UCSD's CSE~118,
%	\emph{Ubiquitous Computing}, taught by Lisa Cowan.
%
%	\item[7/2011] \emph{Introduction to Security}. A technical
%	introduction to several aspects of adversarial thinking
%	including buffer overflows and exploiting TOCTTOU errors. Part
%	of UCSD's CSE~120, \emph{Operating Systems}, taught by Cynthia
%	Taylor.
%
%	\item[4/2010] \emph{Buffer Overflows}. A lecture showing how
%	to perform a buffer overflow on the stack, focusing on using
%	\texttt{gdb} and helper exploit programs to find return
%	addresses in the target program and debugging the exploit.
%	Part of UCSD's CSE~127, \emph{Computer Security}, taught by
%	Hovav Shacham.
%	
%	\item[2/2010] \emph{The Security Mindset}. An introductory
%	lecture describing computer science and beyond with a security
%	mindset. Part of UCSD's CSE~91 \emph{Perspectives in Computer
%	Science}, taught by George Varghese.
%\end{cvseclist}

%\begin{cvseclist}{Teaching Assistant}
%	\item[Summer 2008]
%	\ta{CSE 130: Programming Languages}
%		{http://www-cse.ucsd.edu/classes/su08/cse130/}
%	\ta{CSE 21: Mathematics for Algorithm and System Analysis}
%		{http://www-cse.ucsd.edu/classes/su08/cse21/}
%
%	\item[Spring 2008]
%	\ta{CSE 105: Introduction to the Theory of Computation}
%		{http://www-cse.ucsd.edu/classes/sp08/cse105/}
%
%	\item[Winter 2008]
%	\ta{CSE 105: Introduction to the Theory of Computation}
%		{http://www-cse.ucsd.edu/classes/wi08/cse105/}
%
%	\item[Fall 2007]
%	\ta{CSE 20: Discrete Mathematics}{}
%
%	\item[Summer 2007]
%	\ta{CSE 100: Advanced Data Structures}
%		{http://www-cse.ucsd.edu/classes/su07/cse100/}
%	\ta{CSE 130: Programming Languages}
%		{http://www-cse.ucsd.edu/classes/su07/cse130/}
%	\ta{CSE 141: Computer Architecture}
%		{http://www-cse.ucsd.edu/classes/su07/cse141/}
%	
%	\item[Spring 2007]
%	\ta{CSE 20: Discrete Mathematics}
%		{http://www-cse.ucsd.edu/classes/sp07/cse20/}
%	
%	\item[Winter 2007]
%	\ta{CSE 105: Introduction to the Theory of Computation}
%		{http://www-cse.ucsd.edu/classes/wi07/cse105/}
%	
%	\item[Fall 2006]
%	\ta{CSE 8A: Introduction to Computer Science with Java}{}
%
%	\item[Summer 2006]
%	\ta{CSE 141: Introduction to Computer Architecture}
%		{http://www-cse.ucsd.edu/classes/sp06/cse141}
%	\ta{CSE 141L: Project in Computer Architecture}
%		{http://www-cse.ucsd.edu/classes/sp06/cse141L}
%	\ta{CSE 20: Discrete Mathematics}
%		{http://www-cse.ucsd.edu/classes/su06/cse20}
%	
%	\item[\multilinelabel{Spring 2005\\(UW)}]
%	\ta{CSE 378: Machine Organization and Assembly Language}
%		{http://cs.washington.edu/education/courses/378/05sp/}
%	
%	\item[\multilinelabel{Winter 2005\\(UW)}]
%	\ta{CSE 373: Data Structures and Algorithms}
%		{http://cs.washington.edu/education/courses/373/05wi/}
%	
%	\item[\multilinelabel{Fall 2004\\(UW)}]
%	\ta{CSE 378: Machine Organization and Assembly Language}
%		{http://cs.washington.edu/education/courses/378/04au/}
%\end{cvseclist}

\vfill
\end{cv}
\end{document}
